---
title: "Quakes Pitch"
author: "Juan Carlos Inclán"
date: "4/9/2020"
output: ioslides_presentation
---

## Introduction

The following presentation is about the new app I devolved to know the mean, standard deviation and past locations of quakes in Fiji. Its finality is to give an idea of how devastating is the quakes in Fiji.

In the following slides, will show the origin of the data and the code of the yi.R and server.R

The Shiny app uses the quakes data set from the datasets library in R. The data contains 5 columns that are the following:

1. lat=Latitude of the event
2. long=Longitude of the event
3. depth=Depth (km)
4. mag=Richter Magnitude
5. stations= Number of stations reporting


## ui.R Code
```{r, eval=FALSE}
library(shiny)
library(plotly)

shinyUI(fluidPage(
    titlePanel("Fiji Quakes Plot per location"),
    sidebarLayout(
     sidebarPanel(
         numericInput("numeric", "How many quakes should be plotted?",
                      value=500, min=1, max=1000, step=1),
     ),
    mainPanel(
        h3("Quakes magnitude mean"),
        textOutput("mean1"),
        h3("Quakes magnitude Standard deviation"),
        textOutput("sd1"),
        h3("Fiji's quakes are plotted by longitude and lattitude. The different coloration that is appretiated is due the number of station that reported the quake. This will be useful in a map of Fiji in order to locate where it started."),
        plotlyOutput("plot1")
        )
    )
))
```

## server.R Code
```{r, eval=FALSE}
library(shiny)
library(plotly)

shinyServer(function(input, output){
    
    mean1<-reactive({
        observations<-input$numeric
        mean(quakes$mag[1:observations])
    })
    
    output$mean1<-renderText({
        mean1()
    })
    sd1<-reactive({
        observations<-input$numeric
        sd(quakes$mag[1:observations])
    })
```
***    
```{r, eval=FALSE}   
output$sd1<-renderText({
        sd1()
    })

output$plot1<-renderPlotly({
    number_of_points<-input$numeric
    xlab<-ifelse(input$show_xlab, "Longitude", "")
    ylab<-ifelse(input$show_ylab, "Latitude", "")
    main<-ifelse(input$show_title, "Fiji Quakes axis map", "")
    plot_ly(quakes[1:number_of_points,], x = ~long, y = ~lat, 
    type = "scatter", color = ~factor(stations))
        })    
})

```    




